On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-05-09 manuscripts/IEEE/final_submission.tex
thm 1 changes

\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} If an $n \times \overline m$ matrix $\mathbf{B}$ has for every $i \in [N]$ an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$}, then $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
\begin{align}\label{Cstable}
\|\mathbf{A}_j- (\mathbf{BPD})_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
\end{align}
%
for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}. 
% $\overline m - r(\overline m - m)$

>>>>

\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} The only $n \times \overline m$ matrices $\mathbf{B}$ that have, for every $i \in [N]$, an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} have $\overline m \geq m$, and provided that $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
\begin{align}\label{Cstable}
\|\mathbf{A}_j- (\mathbf{BPD})_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
\end{align}
%
for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}. 
% $\overline m - r(\overline m - m)$
